Discrete Ordinates

### 2016-09-12 docprep/draft1.tex
No change
Fixed the margins on the report

\documentclass{article}
\usepackage{graphicx}
\usepackage{bm}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage[toc,page]{appendix}
\usepackage{listings}
\usepackage{color}
\usepackage{listings}

@@

\begin{equation}
Y_l^m(\theta, \phi) = \sqrt{\frac{2l+1}{4 \pi}
\frac{(l-m)!}{(l+m)!}} P_l^m(\cos \theta) e^{im\phi}
\end{equation}

>>>>

\documentclass{article}
\usepackage{graphicx}
\usepackage{bm}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage[toc,page]{appendix}
\usepackage{listings}
\usepackage{color}
\usepackage{listings}
\usepackage{fullpage}

@@

\begin{equation}\label{eq:spherical_harmonic}
Y_l^m(\theta, \varphi) = (-1)^{l}\sqrt{\frac{2l+1}{4 \pi}
\frac{(l-m)!}{(l+m)!}} P_l^m(\cos \theta) e^{im \varphi}
\end{equation}

Using Euler's Equation (Eq. \ref{eq:euler}) to compute the imaginary exponent, the spherical harmonic can be expanded to Eq. \ref{eq:spherical_harmonic_exp}.

\begin{equation}\label{eq:euler}
e^{i \theta} = \cos(\theta) + i \sin(\theta)
\end{equation}

\begin{equation}\label{eq:spherical_harmonic_exp}
Y_l^m(\theta, \varphi) = (-1)^{l}\sqrt{\frac{2l+1}{4 \pi}
\frac{(l-m)!}{(l+m)!}} P_l^m(\cos \theta) \left[ \cos(m \varphi) + i \sin(m \varphi) \right]
\end{equation}

\begin{equation}\label{eq:spherical_harmonic_xs}
\Sigma_s(\Omega \cdot \Omega') \approx \sum_{l=0}^L \sigma_l \sum_{m=-l}^l Y_l^m(\Omega)\bar{Y}_l^m(\Omega')
\end{equation}

where the over-bar denotes the complex conjugate defined by Eq.~\ref{eq:spherical_harmonic_conj}.

\begin{equation}\label{eq:spherical_harmonic_conj}
\bar{Y}_l^m(\theta, \varphi) = (-1)^{l}\sqrt{\frac{2l+1}{4 \pi}
\frac{(l-m)!}{(l+m)!}} P_l^m(\cos \theta) \left[ \cos(m \varphi) - i \sin(m \varphi) \right]
\end{equation}

Expanding the inner summation of \ref{eq:spherical_harmonic_xs} with Eq.~\ref{eq:spherical_harmonic_exp} and \ref{eq:spherical_harmonic_conj} yields:

\begin{equation}\label{eq:spherical_harmonic_xs_inner}
\begin{split}
Y_l^m(\theta, \varphi)\bar{Y}_l^m(\theta', \varphi') & = 
(-1)^{2l}\frac{2l+1}{4 \pi}
\frac{(l-m)!}{(l+m)!} P_l^m(\cos \theta) P_l^m(\cos \theta') \times \\
&\left[ \cos(m \varphi) + i \sin(m \varphi) \right] \left[ \cos(m \varphi') - i \sin(m \varphi') \right] \\
& = \frac{2l+1}{4 \pi}
\frac{(l-m)!}{(l+m)!} P_l^m(\cos \theta) P_l^m(\cos \theta') \times \\
& \left[ \cos(m \varphi) \cos(m \varphi') + i \sin(m \varphi)\cos(m \varphi') - i \sin(m \varphi') \cos(m \varphi) - i^2\sin(m \varphi) \sin(m \varphi') \right]
\end{split}
\end{equation}
